scRNAseq benchmark in want of a title

### 2019-05-27 bmc_article.tex

We next investigated the impact of different normalization strategies. In addition to log-normalization, the standard Seurat clustering pipeline scales features so that the PCA is not dominated by a small subset of the features, and we therefore included versions of the different normalization, with or without a subsequent scaling (except sctransform's variance-stabilizing transformation, given that, conceptually, it involves something analogous to scaling). Seurat's scaling function includes the option to regress out the effect of certain covariates, and we therefore tested its use with the proportion of mitochondrial counts and the number of detected features. Finally, it has been proposed that the use of stable genes, and in particular cytosolic ribosomal genes, can be used to normalized scRNAseq; we therefore evaluated a simple linear normalization based on the sum of these genes, as well as nuclear genes.

>>>>

We next investigated the impact of different normalization strategies. Beside the standard log-normalization included in Seurat, we tested scran's pooling-based normalization \citep{lunPooling2016}, sctransform's variance-stabilizing transformation \citep{hafemeisterSCtransform2019}, and normalization based on stable genes \citep{linStableGenes2018, deekeStablyExpressed2018}. 
In addition to log-normalization, the standard Seurat clustering pipeline scales features so that the PCA is not dominated by a small subset of the features, and we therefore included versions of the different normalization, with or without a subsequent scaling (except sctransform's variance-stabilizing transformation, given that, conceptually, it involves something analogous to scaling). 
Seurat's scaling function includes the option to regress out the effect of certain covariates, and we therefore tested its use with the proportion of mitochondrial counts and the number of detected features. Finally, it has been proposed that the use of stable genes, and in particular cytosolic ribosomal genes, can be used to normalized scRNAseq; we therefore evaluated a simple linear normalization based on the sum of these genes, as well as nuclear genes.
